Incentivizing Exploration with Unbiased History

### 2018-10-16 algg.tex
rewriting

%!TEX root = main.tex
\section{\ALGG}
We first consider \ALGG which simply shows agents the full history. We discuss in this section the exploration of \ALGG under Assumption \ref{ass:embehave}.

\begin{lemma}
\label{lem:greedy}
There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once. 
\end{lemma}

@@

On the other hand, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once. 
\end{proof}

>>>>

%!TEX root = main.tex
\section{\ALGG: Revealing Full History}

\swedit{Before we describe our algorithms, we will first analyze a
  simple policy \ALGG that fully discloses the history over all
  previous rounds, and lets the agents make the ``greedy'' choices
  across all rounds. Even though the algorithm does not guarantee low
  regret, it will be used as a subroutine in our main algorithms.  In
  particular, we show that because of the randomness in the rewards,
  with constant probability, $\ALGG$ will incentivize the agents to
  play each arm at least once.}

\begin{lemma}
\label{lem:greedy}
Under \Cref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
  on the number of arms $K$.}
\end{lemma}

@@

In addition, we know that this case happens with probability at least
$(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up,
we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds
pulls arm $a$ at least once.
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
